\documentclass[11pt]{article}
\usepackage{hyperref}

\title{My \LaTeX\ Document}
\author{Abdullah Yassine}
\date{\today}

\begin{document}
\tableofcontents
\maketitle % this is to tell it to make the title

This will produce \textit{italized} text.

This will produce \textbf{bold} text.

This will produce \textsc{small caps} text.

This will produce \texttt{typewriter font} text.

Please visit Yassine's website at \url{https://abdullahyassine.me}
or use this \href{https://abdullahyassine.me}{my website}

\vspace{1cm}
Please excuse my dear aunt Sally.

Please excuse my \begin{large}dear aunt Sally.\end{large}

Please excuse my \begin{Large}dear aunt Sally.\end{Large}

Please excuse my \begin{huge}dear aunt Sally.\end{huge}

Please excuse my \begin{Huge}dear aunt Sally.\end{Huge}


\vspace{1cm}


Please excuse my \begin{normalsize}dear aunt Sally.\end{normalsize}

Please excuse my \begin{small}dear aunt Sally.\end{small}

Please excuse my \begin{scriptsize}dear aunt Sally.\end{scriptsize}

Please excuse my \begin{tiny}dear aunt Sally.\end{tiny}

\vspace{1cm}

\begin{center} % this how you center
    This line is centered.
\end{center}



\begin{flushleft} % this how you flushleft
    This line is left aligned..
\end{flushleft}


\begin{flushright} % this how you flushright
    This line is right aligned.
\end{flushright}

% \centering % this center everything that comes after this
% This line is centered.\\
% This line is left-justified.\\
% This line is right-justified.

\vspace{1cm}

% \tiny % this center everything that comes after this
% This line is centered.\\

% This line is left-justified.\\

% This line is right-justified.




% if you do not want numbering on the sections,
% just put * at the end of \section like \section*

\section{Linear Functions} % this how to create functions
    \subsection{Slope-Intercept Form}
        \subsubsection{Example 1}
        \subsubsection{Example 2}
    \subsection{Point-Slope Form}
\section{Quadratic Functions}
    \subsection{Vertex Form}
    \subsection{Standard Form}
    \subsection{Factored Form}

\end{document}